Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-11-14 limits/ms.tex
New sigp and sigpbar plots.
Updated sigp/sigpbar figure captions.

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp_beta.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp_beta.pdf}
\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
  velocity dispersion of the mock data (black).
  }
\label{fig:sigp}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS-sb.pdf}
\caption{{\bf Left:} {\bf JR. Jonathan to add.} The projected velocity dispersion calculated for one model model (extracted from the full ensemble) of the BC Quad with time delays and stellar mass. {\bf Right:} The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper limit of the averaging integral (the aperture size), $a_p$. In both cases, we calculate curves for two extrema velocity anisotropies: $\beta=0$ (green) and $\beta=1$ (red). Over-plotted is the correct answer for the BC model (black) {\bf JR. Jonathan to add}. The stellar half mass radius (yellow) Einstein radius (black) are marked by vertical lines. For this configuration, these two radii are well-separated.}
\label{sigma-beta}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp.pdf}
\caption{
  Estimated projected radially averaged velocity dispersion (\eqnref{eqn:sphericaljeans}) $\sigma_p$ for two Sdom/DMcuspy models ZContrastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $\beta=0$ (blue, solid) and $\beta=1$
  (blue, dashed).  Also shown are the equivalent curves for the mock data after
  running it through the deprojection routines (grey). The solid black line is
  the actual cylindrically averaged velocity dispersion of the original mock particle data.
  The stellar half mass radius (yellow) Einstein
radius (black) are marked by vertical lines. For this configuration, these two
radii are well-separated.}
  \label{fig:sigp} \end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
\caption{{\bf Left:} 
The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
limit of the averaging integral (the aperture size), $a_p$
  for two Sdom/DMcuspy models ZContrastR1R3
  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
  (blue, dashed).  Also shown are the equivalent curves for the mock data after
  running it through the deprojection routines (grey). 
\sout{Over-plotted is the correct answer for the BC model (black)
  {\bf JR. Jonathan to add}.} 
  The stellar half mass radius (yellow) Einstein
radius (black) are marked by vertical lines. For this configuration, these two
radii are well-separated.}
\label{sigma-beta}
\end{figure*}
